Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-04-25 scnn.tex
add figure results
first version of the comparizon of spherical convolution

\subsection{Healpix sampling}

@@

\subsection{Spherical convolutions}
\assign{Nathanaël}

\cite{cohen2017convolutional} 
\cite{cohen2018spherical}
\nati{I meet one of the author of \cite{cohen2018spherical} and we talk for an hour. Here is what I learned}
Very recently, a version of spherical convolutional neural networks have been proposed in~\cite{cohen2017convolutional,cohen2018spherical}. The main goal of this contribution is to develop a CNN with a convolution that is rotation-equivariant on the sphere, i.e. a rotation of the input implies the same rotation of the output. The resulting convolution is performed by a spherical Fourier transform (i.e. a projection on the spherical harmonics), a  multiplication in the spectral domain and an inverse spherical Fourier tranform. The approach is mathematically well justifed and illustrated with a few experiments. The main computational cost of the convultion comes from the two Fourier transforms. The Fourier transform can be accelerated for special samplings set (including the healpix). Nevertheless, even with these acceleration, the convolution seems to be more expensive than graph convolution. A comparizon would be very complicated because the author have focused on \nati{...} sampling set and do not provide any code for the Healpix one.

\cite{boomsma2017spherical}
,
\subsection{Convolutions on graphs}
\assign{Michaël}

@@

In this work, we are using the graph CNN formulation introduced in \cite{defferrard2016convolutional}.

@@

\subsection{Results}
\assign{Nathanaël, Tomek}

>>>>

\todo{
\subsection{Healpix sampling}
Should we have this subsection to explain the advantages of Healpix?
\begin{itemize}
	\item Define the gedesic grid?
	\item reference the "cubed sphere"~\cite{ronchi1996cubed}?
\end{itemize}
}

@@

\subsection{Spherical convolutions} 
The major challenge to generalize CNN to a
spherical domain is to generalize convolution. In the context of CNN, we found
two particular approaches to address this issue.

The first approach, leveraging the continuous spherical convolution, has been
proposed in~\cite{cohen2017convolutional,cohen2018spherical}. These
contributions propose to use a convolution that is rotational equivariant on the
sphere, i.e. a rotation of the input implies the same rotation of the output.
The convolution is performed by a spherical Fourier transform (i.e. a projection
on the spherical harmonics), a  multiplication in the spectral domain and an
inverse spherical Fourier tranform. Hence the main computational cost of a
convolution comes from the two Fourier transforms. Fortunately, the Fourier
transform can be accelerated for special samplings set (theoretically including
HealPix). The main advantage of this approach is that it provides a
mathematically well defined rotational equivariant network. Nevertheless, even
with these Fourier transform acceleration, the convolutions remain expensive in
comparison to a traditional 2D convolution, limiting the practical use of this
approach. While a comparison is theoretically possible, the experiments
of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and
do not provide any code for the Healpix one. Hence, a practical comparison is
not possible.

A second direction has been followed in~\cite{boomsma2017spherical}. The idea is
to use the traditional 2D convolution on an irregular grid defined on the
sphere. In the paper, two grids are used: the geodesic grid and the “cubed
sphere” grid defined by Ronchi et. al~\cite{ronchi1996cubed}. Because this
approach is based on the traditional 2D convolution, it is very likely to be the
most efficient one. However, it suffers that it can only be used using very
specific grid sampling sets which are NOT including HealPix. Furthermore, the
grid requirement makes it impossible for the convolution to capture the
spherical properties of the domain, i.e. the "cubed sphere” sampling is by
definition adapted to a cube and not to a sphere. \nati{Michael: Under some very
specific hypothesis, this second approach is a particular case of our method,
i.e. 1) our method with a stupid sampling, 2) assumption that graph convolution
on a grid == 2d convolution. Do you think we should mention that? I think we
should not.}

In an attempt to get the best of the two approaches, we follow a third
direction. We use a graph to adapt to the particular structure of the sphere.
While the convolution remains efficient, it still captures well the spherical
structure and is particularly adapted to the HealPix sampling.

\subsection{Convolutions on graphs}
\assign{Michaël}

@@

In this work, we are using the graph CNN formulation introduced in~\cite{defferrard2016convolutional}.

@@

\subsection{Results}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.32\textwidth]{figures/result_order1.pdf}
\includegraphics[width=0.32\textwidth]{figures/result_order2.pdf}
\includegraphics[width=0.32\textwidth]{figures/result_order4.pdf}
\caption{Classification errors for the 3 different problems.}
\label{fig:results}
\end{figure}

\assign{Nathanaël, Tomek}
